---
title: "Assignment7_B04704016ªL®a¼Ý"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(fig.width=10, fig.height=8) 
```
```{r, include=FALSE}
library( "dplyr" )
library( "tidyr" )
library( "gridExtra" )
library( "loo" )
library( "rethinking" )
rm(list=ls())
```

# Question 1

```{r, message=FALSE}
# Load data
data( "Hurricanes" )
data <- Hurricanes; rm( Hurricanes )
str( data )

# Create data list for the stan model
model.data <- list(
  N = NROW( data ),
  D = data$deaths,
  C = data$category,
  MP = scale( data$min_pressure )[ ,1],
  DN = scale( data$damage_norm )[ ,1],
  FE = data$female,
  FY = data$femininity
)
str( model.data )

# Model code
stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
}
parameters{
  real a;
}
model{
  vector[N] lamda;
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a;
  }
  D ~ poisson_log( lamda );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a;
    log_lik[i] = poisson_log_lpmf( D[i] | lamda[i] );
  }
}
"

# Fit stan model with model code and model data
fit.stan.0 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.0 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.0 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.0 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.0 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Draw posterior
post.0 <- as.data.frame( fit.stan.0 )

# Recreate lamda and simulate it with new data
f_lamda <- function(x) exp(post.0$a)
femininity_new <- seq( from=min(data$femininity) , to=max(data$femininity) , length.out=30 )

lamda <- 
  sapply(femininity_new, f_lamda) %>%
  as_tibble() %>%
  rename_all(function(x) femininity_new) %>%
  mutate(Iter = row_number()) %>%
  gather(femininity, deaths, -Iter) %>%
  group_by(femininity) %>%
  mutate(hpdi_l = quantile(deaths, probs = 0.055),
         hpdi_h = quantile(deaths, probs = 0.945)) %>%
  mutate(mu = mean(deaths)) %>%
  ungroup() %>%
  mutate(femininity = as.numeric(femininity))

# Plot raw data and model estimate of lamda
p <- ggplot() 
p0 <- p + 
  geom_point(data = data,
             aes(femininity, deaths), 
             shape = 1, color = 'dodgerblue') +
  geom_ribbon(data = lamda,
              aes(x = femininity, ymin = hpdi_l, ymax = hpdi_h), alpha = .5) +
  geom_line(data = lamda,
            aes(x = femininity, y = mu)) +
  ggtitle("Intercept only")

# Model code
stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
}
parameters{
  real a;
  real b_FY;
}
model{
  vector[N] lamda;
  b_FY ~ uniform( -15 , 15 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY * FY[i];
  }
  D ~ poisson_log( lamda );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY * FY[i];
    log_lik[i] = poisson_log_lpmf( D[i] | lamda[i] );
  }
}
"

# Fit stan model with model code and model data
fit.stan.1 <- stan( model_code=stan.model , data=model.data , 
              chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.1 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.1 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.1 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.1 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Draw posterior
post.1 <- as.data.frame( fit.stan.1 )

# Recreate lamda and simulate it with new data
f_lamda <- function(x) exp(post.1$a + post.1$b_FY * x)
femininity_new <- seq( from=min(data$femininity) , to=max(data$femininity) , length.out=30 )

lamda <- 
  sapply(femininity_new, f_lamda) %>%
  as_tibble() %>%
  rename_all(function(x) femininity_new) %>%
  mutate(Iter = row_number()) %>%
  gather(femininity, deaths, -Iter) %>%
  group_by(femininity) %>%
  mutate(hpdi_l = quantile(deaths, probs = 0.055),
         hpdi_h = quantile(deaths, probs = 0.945)) %>%
  mutate(mu = mean(deaths)) %>%
  ungroup() %>%
  mutate(femininity = as.numeric(femininity))

# Plot raw data and model estimate of lamda
p <- ggplot() 
p1 <- p + 
  geom_point(data = data,
             aes(femininity, deaths), 
             shape = 1, color = 'dodgerblue') +
  geom_ribbon(data = lamda,
              aes(x = femininity, ymin = hpdi_l, ymax = hpdi_h), alpha = .5) +
  geom_line(data = lamda,
            aes(x = femininity, y = mu)) +
  ggtitle("Femininity as predictor")

grid.arrange(p0, p1, nrow = 2)
```

## Conclusion

The association between femininity of names and deaths is quite obvious that if we add femininity as a predictor variable, it helps to predict deaths more properly. However, despite the model fits well on most of the cases, it fit poorly on the cases which have high variation.

# Question 2

```{r, message=FALSE}
# Model code
stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
}
parameters{
  real<lower=0> phi;
  real a;
  real b_FY;
}
model{
  vector[N] lamda;
  phi ~ cauchy( 0 , 2 );
  b_FY ~ uniform( -30 , 30 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY * FY[i];
  }
  D ~ neg_binomial_2_log( lamda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY * FY[i];
    log_lik[i] = neg_binomial_2_log_lpmf( D[i] | lamda[i] , phi );
  }
}
"
# Fit stan model with model code and model data
fit.stan.2 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.2 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.2 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.2 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.2 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Draw posterior
post.2 <- as.data.frame( fit.stan.2 )

# Recreate lamda and simulate it with new data
f_lamda <- function(x) exp(post.2$a + post.2$b_FY * x)
femininity_new <- seq( from=min(data$femininity) , to=max(data$femininity) , length.out=30 )

lamda <- 
  sapply(femininity_new, f_lamda) %>%
  as_tibble() %>%
  rename_all(function(x) femininity_new) %>%
  mutate(Iter = row_number()) %>%
  gather(femininity, deaths, -Iter) %>%
  group_by(femininity) %>%
  mutate(hpdi_l = quantile(deaths, probs = 0.055),
         hpdi_h = quantile(deaths, probs = 0.945)) %>%
  mutate(mu = mean(deaths)) %>%
  ungroup() %>%
  mutate(femininity = as.numeric(femininity))

# Plot raw data and model estimate of lamda
p <- ggplot() 
p2 <- p + 
  geom_point(data = data,
             aes(femininity, deaths), 
             shape = 1, color = 'dodgerblue') +
  geom_ribbon(data = lamda,
              aes(x = femininity, ymin = hpdi_l, ymax = hpdi_h), alpha = .5) +
  geom_line(data = lamda,
            aes(x = femininity, y = mu)) +
  ggtitle("Femininity as predictor (gamma Poisson)")

grid.arrange(p1, p2, nrow = 2)
```

## Conclusion

Since the gamma-Poisson distribution assumes that the data has more variation, the coefficient of femininity would have wider range, and thus it overlaps zero.

# Question 3

```{r, message=FALSE}
# Create data list for the stan model
model.data <- list(
  N = NROW( data ),
  D = data$deaths,
  C = data$category,
  MP = scale( data$min_pressure )[ ,1],
  DN = scale( data$damage_norm )[ ,1],
  FE = data$female,
  FY = scale( data$femininity )[ ,1]
)
str( model.data )
stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
  real MP[N];
}
parameters{
  real<lower=0> phi;
  real a;
  real b_FY_MP;
}
model{
  vector[N] lamda;
  phi ~ cauchy( 0 , 2 );
  b_FY_MP ~ uniform( -30 , 30 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_MP * FY[i] * MP[i];
  }
  D ~ neg_binomial_2_log( lamda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_MP * FY[i] * MP[i];
    log_lik[i] = neg_binomial_2_log_lpmf( D[i] | lamda[i] , phi );
  }
}
"
# Fit stan model with model code and model data
fit.stan.3 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.3 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.3 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.3 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.3 , pars=c("log_lik","lamda","lp__"), include=FALSE )

stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
  real DN[N];
}
parameters{
  real<lower=0> phi;
  real a;
  real b_FY_DN;
}
model{
  vector[N] lamda;
  phi ~ cauchy( 0 , 2 );
  b_FY_DN ~ uniform( -30 , 30 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_DN * FY[i] * DN[i];
  }
  D ~ neg_binomial_2_log( lamda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_DN * FY[i] * DN[i];
    log_lik[i] = neg_binomial_2_log_lpmf( D[i] | lamda[i] , phi );
  }
}
"
# Fit stan model with model code and model data
fit.stan.4 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.4 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.4 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.4 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.4 , pars=c("log_lik","lamda","lp__"), include=FALSE )

stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
  real MP[N];
  real DN[N];
}
parameters{
  real<lower=0> phi;
  real a;
  real b_FY_MP_DN;
}
model{
  vector[N] lamda;
  phi ~ cauchy( 0 , 2 );
  b_FY_MP_DN ~ uniform( -30 , 30 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_MP_DN * FY[i] * MP[i] * DN[i];
  }
  D ~ neg_binomial_2_log( lamda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_MP_DN * FY[i] * MP[i] * DN[i];
    log_lik[i] = neg_binomial_2_log_lpmf( D[i] | lamda[i] , phi );
  }
}
"
# Fit stan model with model code and model data
fit.stan.5 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.5 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.5 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.5 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.5 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Calculate WAIC and compare models
log_lik_3 <- extract_log_lik(fit.stan.3, merge_chains = FALSE)
waic_3 <- waic(log_lik_3)
log_lik_4 <- extract_log_lik(fit.stan.4, merge_chains = FALSE)
waic_4 <- waic(log_lik_4)
log_lik_5 <- extract_log_lik(fit.stan.5, merge_chains = FALSE)
waic_5 <- waic(log_lik_5)
compare_model <- loo::compare(waic_3, waic_4, waic_5)
compare_model

# Draw posterior
post.4 <- as.data.frame( fit.stan.4 )
data$femininity_scale <- scale( data$femininity )[ , 1]

# Recreate lamda and simulate it with new data (Male)
f_lamda <- function(x) exp(post.4$a + post.4$b_FY_DN * mean(data[ data$female==0 , ]$femininity_scale) * x)
damage_norm_scale <- scale(data$damage_norm)[,1]
damage_norm_new <- seq( from=min(damage_norm_scale) , to=max(damage_norm_scale) , length.out=30 )

lamda <- 
  sapply(damage_norm_new, f_lamda) %>%
  as_tibble() %>%
  rename_all(function(x) damage_norm_new) %>%
  mutate(Iter = row_number()) %>%
  gather(damage_norm, deaths, -Iter) %>%
  group_by(damage_norm) %>%
  mutate(hpdi_l = quantile(deaths, probs = 0.055),
         hpdi_h = quantile(deaths, probs = 0.945)) %>%
  mutate(mu = mean(deaths)) %>%
  ungroup() %>%
  mutate(damage_norm = as.numeric(damage_norm))

# Plot raw data and model estimate of lamda
p <- ggplot() 
p4_m <- p + 
  geom_ribbon(data = lamda,
              aes(x = damage_norm, ymin = hpdi_l, ymax = hpdi_h), alpha = .5) +
  geom_line(data = lamda,
            aes(x = damage_norm, y = mu)) +
  ggtitle("Counterfactual Plot (Male)")

# Recreate lamda and simulate it with new data (Female)
f_lamda <- function(x) exp(post.4$a + post.4$b_FY_DN * mean(data[ data$female==1 , ]$femininity_scale) * x)
damage_norm_scale <- scale(data$damage_norm)[,1]
damage_norm_new <- seq( from=min(damage_norm_scale) , to=max(damage_norm_scale) , length.out=30 )

lamda <- 
  sapply(damage_norm_new, f_lamda) %>%
  as_tibble() %>%
  rename_all(function(x) damage_norm_new) %>%
  mutate(Iter = row_number()) %>%
  gather(damage_norm, deaths, -Iter) %>%
  group_by(damage_norm) %>%
  mutate(hpdi_l = quantile(deaths, probs = 0.055),
         hpdi_h = quantile(deaths, probs = 0.945)) %>%
  mutate(mu = mean(deaths)) %>%
  ungroup() %>%
  mutate(damage_norm = as.numeric(damage_norm))

# Plot raw data and model estimate of lamda
p <- ggplot() 
p4_f <- p + 
  geom_ribbon(data = lamda,
              aes(x = damage_norm, ymin = hpdi_l, ymax = hpdi_h), alpha = .5) +
  geom_line(data = lamda,
            aes(x = damage_norm, y = mu)) +
  ggtitle("Counterfactual Plot (Female)")

grid.arrange(p4_m, p4_f, nrow = 2)
```

## Conclusion

By comparing WAIC, we could know that the model which considers the interaction between femininity and damage_norm is the mmost plausible. Besides, from the counterfactual prediction plots, we also found that the effect sizes are quite obvious when contrasting the predictions of hurricanes with masculine and feminine names.

# Question 4

```{r, message=FALSE}
# Calculate logarithm of damage_norm
data$log_damage_norm <- log( data$damage_norm )

# Create data list for the stan model
model.data <- list(
  N = NROW( data ),
  D = data$deaths,
  C = data$category,
  MP = scale( data$min_pressure )[,1],
  DN = scale( data$damage_norm )[,1],
  FE = data$female,
  FY = scale( data$femininity )[ ,1],
  LDN = data$log_damage_norm
)
str( model.data )

stan.model <- "
data{
  int<lower=1> N;
  int D[N];
  real FY[N];
  real LDN[N];
}
parameters{
  real<lower=0> phi;
  real a;
  real b_FY_LDN;
}
model{
  vector[N] lamda;
  phi ~ cauchy( 0 , 2 );
  b_FY_LDN ~ uniform( -30 , 30 );
  a ~ uniform( -30, 30 );
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_LDN * FY[i] * LDN[i];
  }
  D ~ neg_binomial_2_log( lamda , phi );
}
generated quantities{
  vector[N] log_lik;
  vector[N] lamda;
  for ( i in 1:N ) {
    lamda[i] = a + b_FY_LDN * FY[i] * LDN[i];
    log_lik[i] = neg_binomial_2_log_lpmf( D[i] | lamda[i] , phi );
  }
}
"
# Fit stan model with model code and model data
fit.stan.6 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Traceplot
traceplot( fit.stan.6 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Show results
print( fit.stan.6 , probs=c(0.055,0.945) , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Plot coeftab
plot( fit.stan.6 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Pairs plot
pairs( fit.stan.6 , pars=c("log_lik","lamda","lp__"), include=FALSE )

# Calculate WAIC and compare models
log_lik_6 <- extract_log_lik(fit.stan.6, merge_chains = FALSE)
waic_6 <- waic(log_lik_6)
compare_model <- loo::compare(waic_4, waic_6)
compare_model
```

## Conclusion

By comparing WAIC values, since the elpd_diff value is negative, we should consider that the model fit.stan.4 is better. It implies that mortality increases linearly with a linear increase in storm strength. Thus, when predicting deaths, we should use damage_norm directly instead of logarithm.

# Question 5

```{r, message=FALSE}
# Load data
data( "bangladesh" )
data <- bangladesh; rm( bangladesh )
str( data )

sort(unique(data$district))
data$district_id <- as.integer( as.factor( data$district ) )
sort(unique(data$district_id))

# Create data list for the stan model
model.data <- list(
  N = NROW( data ),
  N_D = max(data$district_id),
  W = data$woman,
  UC = data$use.contraception,
  LC = data$living.children,
  AC = scale( data$age.centered )[ ,1],
  U = data$urban,
  D = data$district_id
)
str( model.data )

# Traditional fixed-effects model
stan.model <- "
data{
  int<lower=1> N;
  int<lower=1> N_D;
  int D[N];
  int UC[N];
}
parameters{
  vector[N_D] a;
}
model{
  vector[N] p;
  a ~ normal( 0 , 10 );
  for ( i in 1:N ) {
    p[i] = a[D[i]];
  }
  UC ~ binomial_logit( 1 , p );
}
generated quantities{
  vector[N] log_lik;
  vector[N] p;
  for ( i in 1:N ) {
    p[i] = a[D[i]];
    log_lik[i] = binomial_logit_lpmf( UC[i] | 1 , p[i] );
  }
}
"
# Fit stan model with model code and model data
fit.stan.7 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Show results
print( fit.stan.7 , probs=c(0.055,0.945) , pars=c("p","log_lik","lamda","lp__"), include=FALSE )

# Calculate contraception use rate of original data
data.con.rate <- data %>% 
  group_by(district_id) %>% 
  summarise(
    count=n(), 
    total_use_contraception=sum(use.contraception),
    rate=total_use_contraception/count
  ) %>% 
  as.data.frame() %>%
  mutate(
    x_label = reorder(as.factor(paste0('Id=',district_id,'//n=',count)), count)
  )

# Draw posterior
post.7 <- as.data.frame( fit.stan.7 )[,1:60]

p_mean <- as.data.frame( logistic( apply( post.7 , 2 , mean ) ) )
colnames(p_mean) <- c("mu")
p_mean$district_id <- seq( from=1 , to=60 )
p_mean <- as.data.frame( p_mean )

p_PI <- t( as.data.frame( logistic(apply( post.7 , 2, PI , prob=0.89 ) ) ) )
district_id <- seq( from=1 , to=60 )
p_PI <- cbind( p_PI , newColumn=district_id )
colnames(p_PI) <- c("hpdi_l","hpdi_h","district_id")
p_PI <- as.data.frame( p_PI )

# Plot raw data and model estimate of each district
p <- ggplot() 
p7 <- p + 
  geom_point(data = data.con.rate,
             aes(district_id, rate), 
             shape = 1, color = 'dodgerblue') +
  scale_x_discrete(limits = data.con.rate$x_label) + 
  theme(axis.text.x = element_text(angle = 90)) +
  geom_point(data = p_mean,
             aes(district_id, mu), 
             shape = 1, color = 'red') +
  geom_segment(data = p_PI,
              aes(x = district_id, y = hpdi_l, xend = district_id, yend = hpdi_h), alpha = .5) +
  ggtitle("Prediction (Traditional fixed-effects model)")

# Multilevel model
stan.model <- "
data{
  int<lower=1> N;
  int<lower=1> N_D;
  int D[N];
  int UC[N];
}
parameters{
  real mu;
  real<lower=0> sigma;
  vector[N_D] a;
}
model{
  vector[N] p;
  sigma ~ exponential( 1 );
  mu ~ normal( 0 , 10 );
  a ~ normal( mu , sigma );
  for ( i in 1:N ) {
    p[i] = a[D[i]];
  }
  UC ~ binomial_logit( 1 , p );
}
generated quantities{
  vector[N] log_lik;
  vector[N] p;
  for ( i in 1:N ) {
    p[i] = a[D[i]];
    log_lik[i] = binomial_logit_lpmf( UC[i] | 1 , p[i] );
  }
}
"
# Fit stan model with model code and model data
fit.stan.8 <- stan( model_code=stan.model , data=model.data , 
                    chains=4 , cores=4 , iter=2000 )

# Show results
print( fit.stan.8 , probs=c(0.055,0.945) , pars=c("p","log_lik","lamda","lp__"), include=FALSE )

# Draw posterior
post.8 <- as.data.frame( fit.stan.8 )[,1:60]

p_mean <- as.data.frame( logistic( apply( post.8 , 2 , mean ) ) )
colnames(p_mean) <- c("mu")
p_mean$district_id <- seq( from=1 , to=60 )
p_mean <- as.data.frame( p_mean )

p_PI <- t( as.data.frame( logistic(apply( post.8 , 2, PI , prob=0.89 ) ) ) )
district_id <- seq( from=1 , to=60 )
p_PI <- cbind( p_PI , newColumn=district_id )
colnames(p_PI) <- c("hpdi_l","hpdi_h","district_id")
p_PI <- as.data.frame( p_PI )

# Plot raw data and model estimate of each district
p <- ggplot() 
p8 <- p + 
  geom_point(data = data.con.rate,
             aes(district_id, rate), 
             shape = 1, color = 'dodgerblue') +
  scale_x_discrete(limits = data.con.rate$x_label) + 
  theme(axis.text.x = element_text(angle = 90)) +
  geom_point(data = p_mean,
             aes(district_id, mu), 
             shape = 1, color = 'red') +
  geom_segment(data = p_PI,
               aes(x = district_id, y = hpdi_l, xend = district_id, yend = hpdi_h), alpha = .5) +
  ggtitle("Prediction (Multilevel model)")

grid.arrange(p7, p8, nrow = 2)

# Calculate WAIC and compare models
log_lik_7 <- extract_log_lik(fit.stan.7, merge_chains = FALSE)
waic_7 <- waic(log_lik_7)
log_lik_8 <- extract_log_lik(fit.stan.8, merge_chains = FALSE)
waic_8 <- waic(log_lik_8)
compare_model <- loo::compare(waic_7, waic_8)
compare_model
```

## Conclusion

By comparing WAIC values, the multilevel model seems to be better. However, from the prediction plots, we can see that in some districts with less data, the model could fit badly, compared to the fixed-effects model.
